---
title: "Homework assignment 2. Programación y modelación financiera (PMF)"
author: 
  - Lara Hanna Weitgasser A01759114
  - Karina Albarrán A01377604
  - Christian Contreras A00819400
  - María Julia Romero A01114404
  - Melanie Flores A00820434
  - Adriana Beatriz Santos Monterroza A00823399
date: "13/9/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyquant)
library(ggplot2)
library(quantmod)
library(finreportr)
library(tibble)
library(tbl2xts)
library(dplyr)
library(lazyeval)
library(lubridate)
library(tidyverse)
library(tidyr)
library(fpp3)
library(tbl2xts)
library(BatchGetSymbols)
library(forecast)
```

## Asset Pricing 
Risk and return play an important role in making any investment decisions. As we know, the main focus of asset pricing theories is to determine the fundamental value of assets and there is a relation between this and an appropriate return. So, the focus of asset pricing theories is to determine this appropriate return. 
For this report, three U.S. stocks from different industries were selected, which are the following: Nike, Microsoft, and McDonald's Corporation. This assignment includes the last five years of monthly returns for the three individual stocks and the S&P500 stock index. The objective is to provide a comparative analysis of the relationship between asset returns and market. 

## Single-index model 
Determining efficient portfolios within an asset class can be achieved with the Single-index model. The market return is an aggregation of all individual asset returns traded in the stock market. The Single Index Model relates returns on each security to the returns on a common index, such as the S&P500 Stock Index.

### Methodology
The model suggested is:
Ri = αi + βiI + ei
Where:
Ri = expected return on security i
αi = intercept of a straight line or alpha coefficient, component proportional to the market index (βiS&P500j)
βi = slope of straight line or beta coefficient
I = expected return on index (S&P500j)
ei = error term with the mean of zero and a standard deviation which is a constant

This model is the basis for further investigation. As mentioned before, three stocks were selected, i = 1,...3, and 69 monthly returns observations j=1,...69.
Our purpose is to find αi and βi for the stocks of Nike, Microsoft, and McDonald's Corporation. 

## Individual Assets Returns
The stock returns of the past five years for Nike, Microsoft and McDonald's Corporation are the following:

```{r, echo=FALSE, warning=FALSE}
# stock returns
R_stocks <- c("NKE", "MSFT", "MCD") %>%
tq_get(get = "stock.prices", from = "2016-01-01",
to = "2021-10-01") %>%
group_by(symbol) %>%
tq_transmute(select = adjusted,
mutate_fun = periodReturn,
period = "monthly",
col_rename = "R_stocks")
R_stocks
```

## S&P500
Concerning the S&P500, monthly returns for the past five years are:

```{r, echo=FALSE, warning=FALSE}
# S&P500 monthly returns
R_market <- "^GSPC" %>%
tq_get(get = "stock.prices", from = "2016-01-01", to = "2021-10-01") %>%
tq_transmute(select = adjusted,
             mutate_fun = periodReturn,
              period = "monthly",
              col_rename = "R_market")
R_market
```

Here, the S&P500 returns are merged with the three stocks, Nike, Microsoft and McDonald's Corporation, into the same variable.

```{r, echo=FALSE, warning=FALSE}
R_stocks_market <- left_join(R_stocks, R_market, by = c("date" = "date"))
R_stocks_market
```

```{r, echo=FALSE, warning=FALSE}
# All models estimated at once.
R_capm <- R_stocks_market %>%
tq_performance(Ra = R_stocks,
Rb = R_market,
performance_fun = table.CAPM) %>%
select(symbol, Alpha, Beta, `R-squared`)
R_capm
```

From the above table one can observe the results for the single index model estimation for the three stocks. First, let's discuss the beta. There are stocks β from 0.5935 to 0.8628. This can be interpreted as a measure of the volatility, or systematic risk, of a security or a portfolio in comparison to the market as a whole. In other words, beta gives a sense of a stock's market risk compared to the greater market. Beta coefficient is a measure of sensitivity of a share price to movement in the market price. In this case, MCD has the lowest beta so it is less exposed to change in the S&P500, therefore, it can be said that MCD might be exposed to other risk factors, but not at all with the market, this point will be analyzed later in the report. On the other hand, stocks with high betas, as in our case, NKE are highly exposed to changes in the S&P500. Nevertheless, the beta of NKE is less than 1, which means it is less volatile than the whole market. If there was a β that is greater than 1, it would be more volatile than the market, which is not the case here. 

A deeper econometric analysis is needed to validate the above interpretations. All alphas are very close to zero. The R-squared shows what proportion of changes in the stock returns are explained by changes in the stock market, the 47% of MSFT stock return changes are explained by changes in the S&P500

Let's illustrate the previous results in a graphical way.

```{r, echo=FALSE, warning=FALSE}
R_stocks_market$symbol <- factor(R_stocks_market$symbol, levels =
unique(R_stocks_market$symbol))

# Plot all results.
R_stocks_market %>%
ggplot(aes(x = R_market, y = R_stocks, color = symbol)) +
geom_point(alpha = 0.4) +
geom_smooth(method = "lm", se = FALSE) +
facet_wrap(~symbol, ncol = 5) +
geom_abline(intercept = 0, color = "black", linetype = 1) +
theme_minimal() +
labs(x = "SP500 Return", y = "Asset Return",
title = "Relationship between asset return and market") +
theme(legend.position = "none", legend.title = element_blank())
```

```{r, echo=FALSE, warning=FALSE}
R_stocks_market %>%
tq_performance(Ra = R_stocks, Rb = NULL,
performance_fun = table.AnnualizedReturns) %>%
arrange(`AnnualizedSharpe(Rf=0%)`)
```

## Annualized Returns with a Mean Variance Plot 

```{r, echo=FALSE, warning=FALSE}
# Calculate annualized returns.
R_stocks_market_stats <- R_stocks_market %>%
tq_performance(Ra = R_stocks, Rb = NULL,
performance_fun = table.AnnualizedReturns) %>%
# Mean variance plot.
ggplot(aes(x = AnnualizedStdDev, y = AnnualizedReturn, color = symbol)) +
geom_point(size = 5) +
geom_abline(intercept = 0, color = "red") +
geom_text(aes(label = paste0(round(`AnnualizedSharpe(Rf=0%)`, 3))),
vjust = 2, color = "black", size = 3.5) +
geom_text(aes(label = paste0(symbol)),
vjust = -1, color = "black", size = 3.5) + ylim(0, 0.4) +
labs(title = "The higher the risk, the higher the return?",
subtitle = "Numerical values represent return per unit of risk.",
x = "Risk", y = "Return") + theme_tq() +
theme(legend.position = "none", legend.title = element_blank())
R_stocks_market_stats
```

## Portfolio Creation with Equal Weigths

```{r, echo=FALSE, warning=FALSE}
# Weights.
wts <- c(1/3, 1/3, 1/3)
# Portfolio creation.
portfolio_returns_monthly <- R_stocks_market %>%
tq_portfolio(assets_col = symbol,
returns_col = R_stocks,
weights = wts,
col_rename = "Ra")
portfolio_returns_monthly %>%
# Visualization.
ggplot(aes(x = date, y = Ra)) +
geom_bar(stat = "identity", fill = palette_light()[[1]]) +
labs(title = "Portfolio monthly returns.",
subtitle = "10% in each one of the 10 assets.",
caption = "Shows an above-zero trend meaning positive returns.",
x = "", y = "Monthly Returns") +
geom_smooth(method = "lm", color = "red") +
theme_tq() + scale_color_tq() +
scale_y_continuous(labels = scales::percent)
```

## Cumulative Returns

```{r,echo=FALSE, warning=FALSE}
# Cumulative returns.
portfolio_growth_monthly <- R_stocks_market %>%
tq_portfolio(assets_col = symbol,
returns_col = R_stocks,
weights = wts,
col_rename = "investment.growth",
wealth.index = TRUE) %>%
mutate(investment.growth = investment.growth * 10000)
portfolio_growth_monthly %>%
ggplot(aes(x = date, y = investment.growth)) +
geom_line(size = 2, color = palette_light()[[1]]) +
labs(title = "Portfolio growth of $10,000.",
subtitle = "10% in each one of the 10 assets.",
caption = "Now we can really visualize performance!",
x = "", y = "Portfolio Value") +
geom_smooth(method = "loess") +
theme_tq() +
scale_color_tq() +
scale_y_continuous(labels = scales::dollar)
```

## Annualized Returns

```{r,echo=FALSE, warning=FALSE}
# Calculate annualized returns.
R_stocks_market %>%
tq_performance(Ra = R_stocks, Rb = NULL,
performance_fun = table.AnnualizedReturns) %>%
arrange(`AnnualizedSharpe(Rf=0%)`) %>%
left_join(R_capm,by = 'symbol') %>%
select(symbol, `AnnualizedSharpe(Rf=0%)`, Beta)

```

## Comparison between Three Portfolios

```{r, echo=FALSE, warning=FALSE}
weights <- c(
1/3,1/3,1/3, # equally weighted
0.225, 0.325, 0.45,  # sr increasing
0.45, 0.225, 0.325 # beta increasing
)

stocks <- c("NKE", "MSFT", "MCD")
weights_table <- tibble(stocks) %>%
tq_repeat_df(n = 3) %>%
bind_cols(tibble(weights)) %>%
group_by(portfolio)
```

What can be seen above are three different portfolios with different weights which means that in every portfolio the stocks Nike, Microsoft and McDonald's Corporation have different weights in the portfolio. In the first portfolio, the weights are equal, for this reason, every stock weighs 33.33% in the portfolio while in the second, 22.5% is assigned to Nike, 45% to Microsoft and 32.5% to McDonald's Corporation. The ranking is based on the different annualized sharpe ratios of the companies. Since Microsoft had the highest value with 1.9690, it was ranked in first place and Nike with a sharpe ratio of 0.7672 was ranked last. In the third portfolio the ranking was based on the stock's beta value. As a result, Nike was ranked first (45% of portfolio weight) with a beta value of 0.8628, Microsoft second (32.5% of portfolio weight) with a value of 0.8448 and McDonald's Corporation third (22.5% of portfolio weight) with a beta value of 0.5935.

In the next step, the evolution of the three portfolios will be investigated into detail.

## Evolution of the Three Portfolios

```{r, echo=FALSE, warning=FALSE}
# See the evolution of three portfolios.
stock_returns_monthly_multi <- R_stocks_market %>%
tq_repeat_df(n = 3)
portfolio_growth_monthly_multi <- stock_returns_monthly_multi %>%
tq_portfolio(assets_col = symbol,
returns_col = R_stocks,
weights = weights_table,
col_rename = "investment.growth",
wealth.index = TRUE) %>%
mutate(investment.growth = investment.growth * 10000)
portfolio_growth_monthly_multi %>%
ggplot(aes(x = date, y = investment.growth, color = factor(portfolio))) +
geom_line(size = 2) +
labs(title = "Portfolio growth of 10,000.",
subtitle = "1: Equally weighted; 2: Sharpe ratio; 3: Beta",
caption = "Portfolio 2 is a Standout!",
x = "", y = "Portfolio Value",
color = "Portfolio") +
geom_smooth(method = "loess") +
theme_tq() + scale_color_tq() +
scale_y_continuous(labels = scales::dollar)
```

## Conclusion

